\documentclass[10pt, a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{changepage}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage[shortlabels]{enumitem}
\usepackage{microtype, xspace}
\usepackage{hyperref}

\newcommand{\hmargin}{2.5cm}
\geometry{top=1.0cm,
    bottom=2.0cm,
    left=\hmargin,
    right=\hmargin}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan}

\pagenumbering{gobble}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist{topsep=0pt, itemsep=0pt}

% Footer configuration
%--------------------------------------------%
\usepackage{fancyhdr, extramarks}
\pagestyle{fancy}

\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\lfoot{\color{gray}\today}
\cfoot{\color{gray}\textsc{Ryan Selesnik}}

\setlength{\headheight}{14pt} 
%--------------------------------------------%
% End footer configuration

% BEGIN CUSTOM MACROS
% --------------------------------------------- %
\newcommand{\rangesep}{to\xspace}  % for date ranges
\renewcommand{\date}[1]{\textit{#1}}
\newcommand{\location}[1]{\textit{#1}}
\newcommand{\contentType}[1]{\textit{#1}}

\newcommand{\heading}[1]{
\makebox[0pt][l]{\Large \sc \hspace{2pt}#1}
\rule[-0.7ex]{\columnwidth}{0.5pt}\vspace{1.0ex}
}

\newcommand{\subheading}[1]{{\bfseries #1}}
\newcommand{\generalInfoSkip}{\vspace{0.3ex}}
\newcommand{\subheadSkip}{\vspace{0.7ex}}
\newcommand{\contentIndent}{\hspace{1em}}
% --------------------------------------------- %
% END CUSTOM MACROS


% BEGIN CUSTOM ENVIRONMENTS
% --------------------------------------------- %
\newenvironment{mysection}[1]
{\vspace{2.5ex}
\heading{#1}
\begin{adjustwidth}{0.3cm}{0cm}}
{\end{adjustwidth} }

\newenvironment{entry}
\par
{\vspace{0.1ex}}
{}
% --------------------------------------------- %
% END CUSTOM ENVIRONMENTS
\begin{document}

\begin{center}
\textsc{\textbf{\huge Ryan Selesnik}}

\vspace{.2em}
\footnotesize{\textit{Johannesburg, South Africa}}
\\
\vspace{.25em}
\centering
\footnotesize{
\begin{tabular}{c|c|c}

 \href{mailto:selesnikryan@gmail.com}{selesnikryan@gmail.com}     &  \texttt{+}27~799~932252  & \href{https://www.linkedin.com/in/ryan-s-09850613b/}{LinkedIn} 
    
\end{tabular}}

\end{center}

 %
 %    
 % \begin{mysection}{General Information}
 %        \textbf{Citizenship:} South Africa
 %
 %        \generalInfoSkip
 %        \textbf{Fluent languages:} English
 %
 %        \generalInfoSkip
 %            \textbf{Skills include:} A strong programming background in C/C\texttt{++} and Python; Extensive experience simulating control, stochastic, and communication systems using LTspice, \textsc{Matlab}, and \textsc{Simulink}; Data analysis and visualisation using the scientific Python stack (NumPy, Matplotlib, Pandas); Machine Learning with PyTorch, HuggingFace and scikit-learn; Proficient in Bash/Zsh and the Unix core utilities; Working with Linux, macOS, and Windows; Git and GitHub; {\LaTeX}; Arduino and Raspberry Pi; Prototyping and testing with an oscilloscope; Full-stack web development; Automating developer environments with Vim and shell scripts; Experience with multi-threading and concurrent programming in C/C\texttt{++}, Python, Java, and Go.
 %        
% \end{mysection} 
\begin{mysection}{Skills}
    \textbf{Programming:} C/C\texttt{++}, Python, \textsc{Matlab}, Mathematica, Ruby

    \generalInfoSkip
    \textbf{Simulation:} LTspice, \textsc{Simulink}

    \generalInfoSkip
    \textbf{Version Control:} Git, GitHub

    \generalInfoSkip
    \textbf{Data Analysis and Visualisation:} Pandas, NumPy, Matplotlib, 

    \generalInfoSkip
    \textbf{Shell and Unix:} Bash/Zsh, Unix core utilities

\end{mysection}

\begin{mysection}{Education}
        \subheading{The University of the Witwatersrand} \hfill \location{Johannesburg, South Africa}

        \textit{BSc (Eng) Electrical \& Infromation Engineering} (with Distinction) \hfill \date{2019 \rangesep  2022}
            
        \subheadSkip
        \subheading{King David High School, Linksfield} \hfill  \location{Johannesburg, South Africa}

      \textit{National Senior Certificate (Independent Examination Board)} \hfill \date{2014 \rangesep 2018}
    \end{mysection}
\begin{mysection}{Experience}
 \subheadSkip
        \subheading{Stream -- A Division of VAT IT} \hfill \location{Johannesburg, South Africa}

        \textit{Software Engineering Intern}  \hfill \date{Nov 2020 \rangesep Jan 2021}

        \begin{itemize}
            \item Developed a versatile PDF generation system using Ruby, JSON, and Microsoft's Mail Merge.
            \item Enabled non-technical employees to generate customer--specific PDFs, without relying on the software development team, thereby minimising Stream's opportunity costs.
        \end{itemize}   
\subheadSkip
        \subheading{Stream -- A Division of VAT IT} \hfill \location{Johannesburg, South Africa}

        \textit{Software Engineering Intern}  \hfill \date{Dec 2021 \rangesep Jan 2022}

        \begin{itemize}
         \item Wrote a Ruby script to parse PDFs to structured data. This eliminated the tedious task of looking up duty and tax information for imported products.
    \item Developed a customisable message dashboard system using a headless Content Management System, Vue, Node.js, HTML, and CSS, enabling non-technical employees to edit Stream's website directly.
    \item Wrote two sets of comprehensive documentation for the dashboard system. One for the developers and another for the non-technical employees.
        \end{itemize}           
\end{mysection}

\begin{mysection}{Projects}
    
    \subheading{Final Year Investigation Project} \hfill \contentType{Machine Learning}
         
     \begin{itemize}
     \item       Conducted an investigation into a \href{https://github.com/RyanSelesnik/AI-Toy}{low--cost AI toy} that can assist in Early Childhood Development. 

         \item Implemented speech recognition and natural language understanding capabilities using modern ML models such as OpenAI's Whisper and Transformers.
            \item Ported the speech recognition model to a Raspberry Pi and used a children's speech dataset to assess the performance of offline children's speech recognition.
     \end{itemize} 
\subheadSkip   
\subheading{Final Year Design Project} \hfill \contentType{Machine Learning}
 \begin{itemize}
     \item Designed a therapeutic chatbot using GPT-2 and Reinforcement Learning.
     \item Adapted the input context of GPT-2 and used an empathetic reward function as part of the training objective.
 \end{itemize} 

 \subheadSkip
 \subheading{Switch-mode Power Supply} \hfill \contentType{Power/Control Systems, Electronics}
\begin{itemize}
    \item Simulated and built a switch-mode power supply based on the buck converter topology, achieving an output ripple of less than 1\%.
    \item Implemented negative feedback by modulating the duty cycle to ensure a constant output of 5V, independent of the load. 
\end{itemize}

 \subheadSkip
 \subheading{Sensor Measurement Analysis using MPI} \hfill \contentType{Big Data}
\begin{itemize}
    \item Wrote a \href{https://github.com/RyanSelesnik/Big-data-project}{script} to compute statistical indicators for a given data set generated by a sensor in an Inertial Measurement Unit (IMU).
    \item Achieved a speedup of approximately 4x by leveraging Python bindings for the Message Passing Interface (MPI) as well as a computer cluster to parallelize the computation.
\end{itemize}
 \subheadSkip
 \subheading{Temperature Sensor} \hfill \contentType{Embedded Systems}
\begin{itemize}
    \item Designed and built a temperature sensor using the ATmega328P and programmed the logic in Assembly.
\end{itemize}
 \subheadSkip
 \subheading{Multi-player Worlde} \hfill \contentType{Full-stack Web Development}
\begin{itemize}
    \item Collaborated with a team of 5 to develop \href{https://github.com/witseie-elen4010/2022-group-lab-001}{MultiWordle}, a multiplayer version of Wordle. The tech--stack included JavaScript, Express, HTML, CSS, GitHub Actions, and MongoDB. 
\end{itemize}
 \subheadSkip

 \subheading{Centipede\texttt{++}} \hfill \contentType{Software Development}
\begin{itemize}
    \item Collaborated with a team of 2 to develop the Centipede computer game in C\texttt{++}.
\end{itemize}


\end{mysection}

\begin{mysection}{Honours and Awards}
\subheadSkip
\subheading{Isazi Prize} \hfill \location{University of the Witwatersrand}


\hspace{1em} Awarded to the top 5 information engineering students who achieved an aggregate of 70\% and above in their third year of study.

\subheadSkip
\subheading{The Dean's List} \hfill \location{University of the Witwatersrand}

\hspace{1em} The Dean's list recognises the top 10\% of students provided that a minimum average/aggregate of at least 70\% is obtained on a full curriculum.

\subheadSkip
\subheading{Wits Mathematics Competition} \hfill \location{University of the Witwatersrand}

\hspace{1em} Selected to represent King David High School, Linksfield  at the Wits mathematics competition in 2018. 

\end{mysection}


\end{document}
